An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-05-27 poly-embed-journal/poly-embed-journal.tex

\begin{restatable}{theorem}{calibratedseparated} \label{thm:calibrated-separated}
  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$, discrete loss $\ell:\R\to\reals^\Y_+$, and link $\psi:\reals^d\to\R$ be given.
  Then $(L,\psi)$ is calibrated with respect to $\ell$ if and only if
  $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ for some
  $\epsilon>0$.
\end{restatable}
Intuitively, a separated link is calibrated because of two facts.
First, Lemma~\ref{lem:polyhedral-range-gamma} states that a polyhedral surrogate has only a finite number of ``optimal report sets'' $\{\Gamma(p) : p \in \simplex\}$.
Second for a given $p$, the expected surrogate loss for a suboptimal point scales with the distance from the optimal set $\Gamma(p)$ at some minimum linear rate $\alpha > 0$; this rate is related to \emph{Hoffman constants}.
Combining with the first fact gives a universal minimum constant $\alpha$ for all $p$.
Now bringing in $\epsilon$-separation, any surrogate report linking to a suboptimal target report has expected surrogate loss at least $\alpha \cdot \epsilon > 0$.
On the other hand, if a link is not separated, then the same two facts imply that a sequence of surrogate reports that get arbitrarily close to an optimal report set while linking to a suboptimal target report; this sequence has expected loss approaching optimal, violating calibration.

@@

Given the above proof sketch, the following construction is relatively straightforward.
We initialize the link using the embedding points and optimal report sets, then adjust $\Psi$ to narrow down to only legal choices; we then pick from $\psi(u)$ from $\Psi(u)$ arbitrarily.
Theorem \ref{thm:thickened-separated} implies that, for all small enough $\epsilon$, the resulting link $\psi$ is well-defined at all points, and $\epsilon$-separated.
\begin{construction}[$\epsilon$-thickened link] \label{const:eps-thick-link}
  Given a polyhedral $L$ that embeds some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  First, define $\U = \{\Gamma(p) : p \in \simplex\}$.
  % For each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$. \jessiet{Move this sentence below link envelope definition?}
  First, initialize the \emph{link envelope} $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$, where $R_U = \{r \in \R : \varphi(r) \in U\}$ is the set of target reports that embed into $U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{construction}

>>>>

\begin{restatable}{theorem}{calibratedseparated} \label{thm:calibrated-separated}
  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$, discrete loss $\ell:\R\to\reals^\Y_+$, and link $\psi:\reals^d\to\R$ be given.
  Then $(L,\psi)$ is calibrated with respect to $\ell$ if and only if
  $\psi$ is $\epsilon$-separated with respect to $L$ and $\ell$ for some
  $\epsilon>0$.
\end{restatable}
Intuitively, a separated link is calibrated because of two facts.
First, Lemma~\ref{lem:polyhedral-range-gamma} states that a polyhedral surrogate has only a finite number of ``optimal report sets'' $\{\Gamma(p) : p \in \simplex\}$.
Second, for a given $p$, the expected surrogate loss for a suboptimal point scales with the distance from the optimal set $\Gamma(p)$ at some minimum linear rate $\alpha > 0$; this rate is related to \emph{Hoffman constants}.
Combining with the first fact gives a universal minimum constant $\alpha$ for all $p$.
Now bringing in $\epsilon$-separation, any surrogate report linking to a suboptimal target report has expected surrogate loss at least $\alpha \cdot \epsilon > 0$.
On the other hand, if a link is not separated, then the same two facts imply that, for a sequence of surrogate reports that get arbitrarily close to an optimal report set while linking to a suboptimal target report, this sequence has expected loss approaching optimal, violating calibration.

@@

Given the above proof sketch, the following construction is relatively straightforward.
We initialize the link using the embedding points and optimal report sets, then adjust $\Psi$ to narrow down to only legal choices; we then pick from $\psi(u)$ from $\Psi(u)$ arbitrarily.
Theorem \ref{thm:thickened-separated} implies that, for all small enough $\epsilon$, the resulting link $\psi$ is well-defined at all points, and $\epsilon$-separated.
\begin{construction}[$\epsilon$-thickened link] \label{const:eps-thick-link}
  Given a polyhedral $L$ that embeds some $\ell$ via the embedding $\varphi: \Sc \to \reals^d$ for a representative set $\Sc$; and given an $\epsilon > 0$ and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  Define $\U = \{\Gamma(p) : p \in \simplex\}$.
  % For each $U \in \U$, let $R_U = \{r \in \R : \varphi(r) \in U\}$, the reports whose embedding points are in $U$. \jessiet{Move this sentence below link envelope definition?}
  First, initialize the \emph{link envelope} $\Psi: \reals^d \to 2^{\Sc}$ by setting $\Psi(u) = \Sc$ for all $u$.\botodo{$\Psi$ maps to $2^{\Sc}$ because $\Psi(u) = \emptyset$ sometimes}
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$, where $R_U = \{r \in \Sc : \varphi(r) \in U\}$ is the set of target reports that embed into $U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{construction}
